Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2020-09-09 paper/ifo-introduction.tex

% continuous gws
To date, the network of gravitational-wave observatories has detected numerous signals from binary black hole~\cite{GW151226,GW170104,GW170814} and binary neutron star~\cite{GW170817,GW170817multi,GW190425} mergers, short-duration transient signals~\cite{GWTC-1:2018,GWOSC:online}. 
However, the network is also searching for continuous gravitational waves: persistent, periodic, near-monochromatic signals, but is as yet unsuccessful~\cite{ScoX1O2Viterbi:2019,RadiometerO1O2:2019,SearchCrossCorrO1:2017,ScoX1ViterbiO1:2017,SearchRadiometerO1:2017,SearchCrossCorrO1:2017,MiddletonEtAlO2LMXBs:2020,SearchTwoSpecS6:2017}.
Predicted sources for such continuous (gravitational) waves include rotating neutron stars in orbit around low mass stellar companions (e.g.\ low mass X-ray binaries, LMXBs). Continuous waves from such sources may be emitted at constant frequency or may wander slowly in frequency over time. 
For example, the rotation frequency of a neutron star in a LMXB can wander over time due to variable accretion of matter (and hence angular momentum transfer) from the stellar companion~\cite{xraybinaries:1997}, and this rotation frequency is predicted to determine the frequency of the continuous waves.
The prime target for continuous wave searches from LMXBs is Scorpius X-1, an LMXB particularly bright in X-rays.

>>>>

% continuous gws
To date, the network of gravitational-wave observatories has detected at least ten signals from binary black hole mergers~\cite{GW151226,GW170104,GW170814,GWTC-1:2018} and at least one from a binary neutron star merger~\cite{GW170817,GW170817multi,GW190425, GWTC-1:2018}, all short-duration transient signals~\cite{GWTC-1:2018,GWOSC:online}. 
However, the network is also searching for continuous gravitational waves: persistent, periodic, near-monochromatic signals, but is as yet unsuccessful~\cite{ScoX1O2Viterbi:2019,RadiometerO1O2:2019,SearchCrossCorrO1:2017,ScoX1ViterbiO1:2017,SearchRadiometerO1:2017,SearchCrossCorrO1:2017,MiddletonEtAlO2LMXBs:2020,SearchTwoSpecS6:2017}.
Predicted sources for such continuous (gravitational) waves include rotating neutron stars in orbit around low mass stellar companions (e.g.\ low mass X-ray binaries, LMXBs). Continuous waves from such sources may be emitted at constant frequency or may wander slowly in frequency over time. 
For example, the rotation frequency of a neutron star in a LMXB can wander over time due to variable accretion of matter (and hence angular momentum transfer) from the stellar companion~\cite{xraybinaries:1997}, and this rotation frequency is predicted to determine the frequency of the continuous waves.
The prime target for continuous wave searches from LMXBs is Scorpius X-1, an LMXB particularly bright in X-rays.
